 

### 2020-09-03 vertical-thermal-review.Rmd
Revert "Revert "Revert "Merge branch 'master' of https://github.com/EcoClimLab/vertical-thermal-review"""
This reverts commit 046938c584cecbc377ce2656c32446dedca962b1.

**Table 1. Summary of observed variation in thermally-relevant leaf traits with canopy height and/or between sun and shade leaves** ([*GitHub issue #9*](https://github.com/EcoClimLab/vertical-thermal-review/issues/9))

@@

**Table 2. Summary of observed variation in leaf metabolism and thermal responses across the vertical gradient and/or between sun and shade leaves** ([*GitHub issue #9*](https://github.com/EcoClimLab/vertical-thermal-review/issues/9))

>>>>

![(*For latest version of table, see tables.pdf.*)](table1.png)

@@

![(*For latest version of table, see tables.pdf.*)](table2.png)

*Stomatal conductance*

*Photosynthesis*
